---
title: "Assignment 1"
---

# Assignment 1

My first assignment is has two parts.First part about a talk conducted with the contributions of Erdi Daşdemir and Baykal Hafızoğlu. Baykal Hafızoğlu is the main speaker of the talk. He completed his undergraduate and graduate studies in Turkey, earned his PhD at Arizona State University in the USA, and currently works at FICO in the USA. In the first step of my assignment, I will provide a brief summary of the talk and I will present two different questions about the talk along with their answers.

## (a)Brief Summary of Hafızoğlu's Speech:

In the seminar, many important insights related to academic and professional development were shared. Hafızoğlu emphasized how valuable mathematical modeling and coding skills are in the business world. He highlighted that learning programming languages like Python, especially starting at a young age, would be a great advantage in the future. Additionally, he explained that pursuing a PhD leaves a strong impression during job interviews in terms of technical proficiency and helps to develop problem-solving skills. However, he noted that while a PhD is not necessary for every professional, it can provide a significant advantage in career progression. Lastly, he stressed the importance of conducting literature reviews and working with more advanced methods, which becomes unavoidable, particularly at the master’s and PhD levels.

**1-)**How can mathematical modeling and coding skills, such as those learned in Python, contribute to solving complex industrial engineering problems in the real world?

**Answer:**\
Mathematical modeling and coding skills allow engineers to create precise models of real-world processes, enabling optimization, simulation, and prediction of outcomes. By using programming languages like Python, engineers can automate data analysis, apply machine learning techniques, and solve complex optimization problems more efficiently. This combination of skills is particularly valuable for addressing challenges such as resource allocation, process efficiency, and predictive maintenance in industrial settings.

2-)Which of the following is NOT a reason why Hafızoğlu emphasized the importance of learning programming languages like Python at an early age?

A\) It provides a significant advantage in future problem-solving tasks.\
B) It helps develop communication skills in a professional environment.\
C) It enhances the ability to tackle mathematical modeling tasks efficiently.\
D) It builds a strong foundation for technical proficiency in various industries.

**Answer:**\
**B)** It helps develop communication skills in a professional environment.

Hafızoğlu did not mention relation between Phyton and communication skills.

## (b)Polls_us_election_2016:
```{r}
library(dslabs)
data("polls_us_election_2016")
polls_us_election_2016[1:10, ]
```
Here is the first ten column of our data.And here is the number of NA values:
```{r}
sum(is.na(polls_us_election_2016))
```
Now we will replace all NA values in the “polls_us_election_2016” data set as follows: For numeric columns, we will replace NA values with 2001. For character or factor columns,we will  replace NA values with Barış.After that 
we willstore the modified data set as a new object.
```{r}
no_nas<- polls_us_election_2016
birth_year<-2001
first_name<-'baris'
for (col in names(no_nas)){
  if(is.numeric(no_nas[[col]])){
    no_nas[[col]]<-ifelse(is.na(no_nas[[col]]),birth_year,no_nas[[col]])
  }
  else if(is.character(no_nas[[col]])|| is.factor(no_nas[[col]])){
    no_nas[[col]]<-ifelse(is.na(no_nas[[col]]),first_name,as.character(no_nas[[col]]))
   }
  }
```
This must be do it.Let's check the results:
```{r}
sum(is.na(no_nas))
no_nas[1:10, ]
```
